Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-27 tex/ms.tex
figure 1 of ms

\clearpage
\begin{figure}
  \begin{center}
    [\hogg{PUT FIGURE HERE}]
  \end{center}
  \caption{An example of why this project is necessary.  The points are... \hogg{this should be a figure showing heavily censored data and a traditional fit to them, folded AND UNFOLDED, showing that the traditional fit is way wrong.}\label{fig:badfit}}
\end{figure}

>>>>

\clearpage
\begin{figure}
  \begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/fig_045832-0604_1.png}
  \end{center}
  \caption{A comparison of the best fit obtained by the traditional method (left) and our censored data model (right) on the Mira variable ASAS 045832-0604.1.  The top row shows the respective model fits to the raw light curves while the bottom row displays the period-folded data and models.  The black dots denote the observed data and the red vertical dashes mark the epochs of null observation.  The traditional fitting method clearly obtains half the true period while our method recovers the correct period.  The traditional method fails because it identifies a reasonable high-frequency fit to the observed data which completely ignores the null observations.  Note that alternate cycles of the traditional model fit contain no observed data.  By contrast, our method fully accounts for the null observations using a probability model.\label{fig:badfit}}
\end{figure}
